Profit Optimisation in Heterogeneous 2-link Parallel Games

### 2024-11-27 thesis/article.tex
Thesis: Generalises split function chapter for n-links, also Preliminaries improvements

In the homogeneous case all players have an equal reaction to tolls, and therefore the effective cost of a player using link $i$ becomes $\ell_i(x_i) + t_i$.
For a given set of tolls $t$, a flow $x$ is a \textit{Wardrop equilibrium for $t$} if $\forall i, j \in N$ with $x_i > 0$ it holds that
\begin{equation*}
	\ell_i(x_i) + t_i \leq \ell_j(x_j) + t_j
\end{equation*}
In that case, all links with $x_i > 0$ have equal effective costs, i.e. there exists some $K > 0$ such that $\ell_i(x_1) + t_i = K$ for all links $i$ with $x_i > 0$.
From a well-known result from Beckman et al. \cite{beckmann1956studies} and Dafermos and Sparrow \cite{1363388843888284416}, such and an equilibrium for $t$ exists, is unique with regard to costs and can be described by the following inequality.
\begin{lemma}
	\label{lemma:wardrop_equilibrium}
	A flow $x$ is a Wardrop equilibrium for $t$ if and only if for all feasible flows $x^\prime$,
	\[\sum_{i \in N} (\ell_i(x_i) + t_i) \cdot (x_i - x_i^\prime) \leq 0\]
\end{lemma}

We can therefore denote by $x(t)$ the flow occurring on that unique equilibrium for a given toll $t$.
If $t = 0$ then the equilibrium is called the \textit{Wardrop equilibrium}.
It's also worth noting that looking at Lemma \ref{lemma:wardrop_equilibrium}, we can see that what actually matters, with regard to the flow, is the relative difference among the tolls, and not their actual values.
To demonstrate this, if we consider an arbitrary $c \in \R_+$ and tolls $t^\prime = t + c$ then for the same flow $x$ and any other flow $x^\prime$ the sum becomes
\begin{flalign*}
	\sum_{i \in N} (\ell_i(x_i) + t_i + c) (x_i - x_i^\prime) &= \sum_{i \in N} (\ell_i(x_i) + t_i) (x_i - x_i^\prime) + c \left(\sum_{i \in N} x_i - \sum_{i \in N} x_i^\prime\right) \\
	&= \sum_{i \in N} (\ell_i(x_i) + t_i) (x_i - x_i^\prime) \leq 0
\end{flalign*}
which makes $x$ the Wardrop equilibrium for $t^\prime$ as well.
The last equality holds because $x_i, x_i^\prime$ are flows of the network and therefore $\sum_{i \in N} x_i = \sum_{i \in N} x_i^\prime = 1$.
Also, this reasoning is still valid for $c < 0$ as long as $t_i + c \ge 0$ for all $i \in N$, or in other words, as long as $c \ge -\min_{i \in N}{t_i}$.

Finally for affine latencies we can calculate $x(t)$.
For $\ell_i(x_i) = a_i x_i + b_i$ with $a_i > 0, b_i \geq 0$ and $t \in \R_+^N$, define $N(t) = \{i \in N | x_i(t) > 0\}$.
Since $x(t)$ is an equilibrium for $t$ then for all $i \in N(t)$ we get $\ell_i(x_i) + t_i = K$ for some common efficient cost $K$.
By also using the fact that $\sum_{j \in N(t)} x_i = 1$ we solve the equations with regard to $K$ and eventually we get for all $i \in N(t)$
\begin{equation}
	\label{eq:homogeneous_x_i}
	x_i(t) = \frac{1 + \sum_{j \in N(t)}\frac{b_j + t_j - b_i - t_i}{a_j}}{\sum_{j \in N(t)}\frac{a_i}{a_j}}
\end{equation}

It is important to note here that formula \ref{eq:homogeneous_x_i} is valid only for $t$ such that the result is in $[0, 1]$.
If we allow any arbitrary $t \in \R_+^N$ then we can find extreme instances of the game, which wouldn't occur in the optimal play of the link owners anyway.
For example, if for tolls $t$ link owner $i$ has $t_i$ large enough such that $x_i(t) = 0$, then for any $t_i^\prime > t_i$ it also holds that $x_i(t_i^\prime, t_{-i}) = 0$, while formula \ref{eq:homogeneous_x_i} would decrease.
Since we assume that link owners play optimally, we will also assume that tolls $t$ are within the bounds where formula \ref{eq:homogeneous_x_i} is valid.

@@

For homogeneous players and affine latencies we can calculate the best response functions $B_i(t_{-i})$.
For each link owner $i$, by solving first order conditions on $\Pi_i(t_i, t_{-i})$ for $t_i$ we get
\begin{equation}
	\label{eq:homogeneous_br_i}
	B_i(t_{-i}) = \frac{1 + \sum_{j \in N(t) : j \ne i}\frac{b_j + t_j - b_i}{a_j}}{\sum_{j \in N(t) : j \ne i}\frac{2}{a_j}}
\end{equation}

Similarly to \ref{eq:homogeneous_x_i}, this formula is valid only for tolls in a bounded subset of $\R_+^N$.

@@

We finish this section with a crucial property for homogeneous pricing games that we will need later.
\begin{lemma}
	\label{lemma:tolls_diff}
	Let $(N, \ell, 1)$ be a homogeneous pricing game, and let $D_i$ a function for each link $i$ where $D_i(t_{-i}) = B_i(t_{-i}) - t_{-i}$, a vector of $t_i - t_j$ values for all $t_j \in t_{-i}$.
	Then $D_i$ is decreasing with regard to any $t_j \in t_{-i}$.
\end{lemma}

\begin{proof}
	For any link $i$ and any $t_j \in t_{-i}$ consider the respective element of $D_i$, which is $B_i(t_{-i}) - t_j$.
	From formula \ref{eq:homogeneous_br_i} after some calculations we get
	\[
		B_i(t_{-i}) - t_j = \left(\frac{1}{\sum_{k \ne i} \frac{2a_j}{a_k}} - 1\right)t_j + \frac{1 + \frac{b_j - b_i}{a_j} + \sum_{k \ne i, j}\frac{b_k + t_k - b_i}{a_k}}{\sum_{k \ne i} \frac{2}{a_k}}
	\]
	which decreasing with regards to $t_j$ if and only if its coefficient is negative.
	Indeed, since $a_i > 0$ for all $i$, we get
	\[
		\frac{1}{\sum_{k \ne i} \frac{2a_j}{a_k}} - 1 = \frac{1}{2 \left(1 + \sum_{k \ne i, j} \frac{a_j}{a_k}\right)} - 1 \leq \frac{1}{2} - 1 < 0
	\]
\end{proof}

@@

Consider a $([2], \ell, \alpha)$ toll game such that $x_1(0), x_2(0) > 0$ with tolls $t = (t_1, t_2)$ assigned to them and  $x(t) = (x_1(t), x_2(t))$ the Nash equilibrium for $t$.
Without loss of generality we assume $t_1 > t_2$ which from Lemma \ref{lemma:latencies_tolls} follows that $\ell_1(x_1(t)) < \ell_2(x_2(t))$.
For the $2$ edges of the game we introduce the term money sensitivity split $\as(t)$ as the value of $\alpha$ for which if any player $p$ has $\alpha(p)=\as(t)$ then that player sees the $2$ edges' total latencies as equal.
More specifically, $\as(t)$ is the value of the distribution function $\alpha$ for which it holds
\[\ell_1(x_1(t)) + \as(t) \cdot t_1 = \ell_2(x_2(t)) + \as(t) \cdot t_2\]
Solving for $\as$ we get
\[\as(t) = \frac{\ell_2(x_2(t)) - \ell_1(x_1(t))}{t_1 - t_2}\]
\\
Before we get into a more formal definition and description of $\as$, it'd help to first discuss the nature of the split that $\as$ captures.
Regardless of whether there exists a player $p$ such that $\alpha(p) = \as(t)$, it still holds that
\begin{itemize}
	\item if $\alpha(p) < \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 < \ell_2(x_2(t)) + \alpha(p \cdot) t_2$, thus $p$ is on edge $1$
	\item if $\alpha(p) > \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 > \ell_2(x_2(t)) + \alpha(p) \cdot t_2$, thus $p$ is on edge $2$
	\item if $\alpha(p) = \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 = \ell_2(x_2(t)) + \alpha(p) \cdot t_2$, thus $p$ is either on edge $1$ or $2$
\end{itemize}
Remember that we have assumed that $t_1 > t_2 \Rightarrow \ell_1(x_1(t)) < \ell_2(x_2(t))$.
Therefore the flow passing through the faster edge $1$ is contained with players where $\alpha(p) \le \as(t)$, while the flow in the cheaper edge $2$ is contained with players where $\alpha(p) \ge \as(t)$.
Since the players are sorted in increasing order according to $\alpha$, it helps to view the players in the first case as the "lower" part of the split and respectively the players in the second case as the "upper" part of the split.
If it helps with the intuition, alternative split labels could be rushed-relaxed or rich-poor.
Table \autoref{table:split_summary} provides of a summary for each part of the split

@@

\begin{definition}
	\label{definition:split_function}
	Given a $([2], \ell, \alpha)$ toll game with $x_1(0), x_2(0) > 0$, tolls $t = (t_1, t_2), t_1 \ne t_2$ and $x(t) = (x_1(t), x_2(t))$ the Nash equilibrium for $t$, we define the \textit{money sensitivity split function} $\as: \R_+^2 \setminus \{(a, a) | a \in \R_+\} \rightarrow (0, +\infty)$ as follows 
	\[\as(t) = \frac{\ell_2(x_2(t)) - \ell_1(x_1(t))}{t_1 - t_2}\]
\end{definition}

We will also give a more formal definition to the lower-upper split intuition we described above.
\begin{definition}
	\label{definition:split_lower_upper}
	Given a $([2], \ell, \alpha)$ toll game with $x_1(0), x_2(0) > 0$, tolls $t \ne 0$ and $x(t)$ the Nash equilibrium for $t$, and also assuming w.l.o.g. that $t_1 > t_2$, we define as \textit{lower split} the (possibly zero) flow $x_1(t)$ and as \textit{upper split} the remaining flow $x_2(t)$. 
\end{definition}

\begin{corollary}
	\label{corollary:split_to_alpha}
	Given a $([2], \ell, \alpha)$ toll game with $x_1(0), x_2(0) > 0$ and tolls $t \ne 0$, it holds that
	\begin{itemize}
		\item $\alpha(p) \le \as(t)$, for all players $p$ in the lower split
		\item $\alpha(p) \ge \as(t)$, for all players $p$ in the upper split
	\end{itemize}
\end{corollary}

\begin{proof}
	Let again w.l.o.g. assume $t_1 > t_2 \LeftrightarrowArg{\ref{lemma:latencies_tolls}} \ell_1(x_1(t)) < \ell_2(x_2(t))$, making by definition \ref{definition:split_lower_upper} a player $p$ in the lower split be in link $1$.
	Since $x$ is a Nash equilibrium we have
	\begin{align*}
		c_1^p(t) &\le c_2^p(t) \Rightarrow \ell_1(x_1(t)) + \alpha(p) \cdot t_1 \le \ell_2(x_2(t)) + \alpha(p) \cdot t_2 \\
		&\RightarrowArg{t_1 > t_2} \alpha(p) \le \frac{\ell_2(x_2(t)) - \ell_1(x_1(t))}{t_1 - t_2} \RightarrowArg{\ref{definition:split_function}} \alpha(p) \le \as(t)
	\end{align*}
	Similarly we can show that $\alpha(p) \ge \as(t)$, for all players $p$ in the upper split.
\end{proof}

At this point in our analysis, we will additionally need the notion of the lowest and highest $\alpha$ value in a flow of players.

In general, since we're working with a Lebesque-measurable flow, it is natural to not bother with distinguishing between a flow $[0, x_1]$ or $[0, x_1)$, as the player $x_1$ can be arbitrarily placed at any link without affecting the game.
In a heterogeneous setting, however, the existence or not of that player matters, as its $\alpha(x_1)$ value might be different from the rest of the players in the flow, depending on how $\alpha$ is defined.
We bypass this issue by instead using set border bounds.

\begin{definition}
	\label{definition:alpha_flow_sets}
	Let $([2], \ell, \alpha)$ a toll game with $x_1(0), x_2(0) > 0$, tolls $t \ne 0$ and $x(t)$ the Nash equilibrium for $t$.
	We define as $A_i(t)$ the set of $\alpha(p)$ values for players $p$ on edge $i$ in the Nash equilibrium for $t$.
	More formally, we define a set function $A_i: \R_+^2 \setminus \{(a, a) | a \in \R_+\} \rightarrow \mathcal{P}(\R_+)$ such that
	\[A_i(t) = \{\alpha(p)|p \text{ in edge } i \textit{ for } x(t) \}\]
	For tolls where $t_1 = t_2$ we cannot define lower and upper split, but we will extend the definition of $A_i$ for those tolls with a sign to specify which split we assume the link to have.
	Therefore we define $A_i^-(0)$ and $A_i^+(0)$ respectively as
	\[A_i^-(0) = \{\alpha(p)|p \in [0, x_i(0))\} \qquad A_i^+(0) = \{\alpha(p)|p \in (x_i(0), 1]\}\]
	%\[A_i^-(0) = \lim_{t_1 - t_2 \rightarrow 0^-}A_i(t) \qquad A_i^+(0) = \lim_{t_1 - t_2 \rightarrow 0^+}A_i(t)\]
\end{definition}

We ignore all $\alpha(x_i(0))$ values in order to avoid any confusion, since they are arbitrarily placed in any edge and their $\alpha$ value could change the sets' properties.
It doesn't affect our analysis, however, since having a split on that player is only possible for $t = 0$ and $\as(0)$ is undefined, plus as we'll show in the next section neither it's limit exists, making the $\alpha$ value of player $x_i(0)$ (in each assumingly split case) irrelevant.

We continue with describing some basic properties around the values of $\as$.

@@

\begin{lemma}
	\label{lemma:split_basic}
	Given a $([2], \ell, \alpha)$ toll game with $x_1(0), x_2(0) > 0$ and tolls $t \ne 0$, the following hold:
	\begin{enumerate}[(i)]
		\item $\as(t) > 0$
		\item if $x_1(t), x_2(t) > 0$ then $\as(t) \in [\alpha(0), \alpha(1)]$
		\item if $\as(t) < \alpha(0)$ or $\as(t) > \alpha(1)$ then $x(t) = (0, 1)$ or $(1, 0)$
		\item if $x_1(t), x_2(t) > 0$ with $\ell_1(x_1(t)) < \ell_2(x_2(t))$ then\\
		$\sup A_1(t) \le \as(t) \le \inf A_2(t)$
	\end{enumerate}
\end{lemma}

\begin{proof}
	$ $ % Just to make a line break after "Proof".
	\begin{enumerate}[(i)]
		\item Trivial application of Lemma \ref{lemma:latencies_tolls}.
		Since we have $t_1 \ne t_2$ it follows that $\ell_1(x_1(t)) \ne \ell_2(x_2(t))$ and therefore $\as(t) \ne 0$.
		Then we only need to notice that $\ell_1(x_1(t)) < \ell_2(x_2(t)) \Leftrightarrow t_1 > t_2$ and we get $\as(t) > 0$ from Definition \ref{definition:split_function}.
		\item Since $x_1(t), x_2(t) > 0$ then $\exists p_1, p_2 \in [0, 1]$ each on a different link, for which we assume w.l.o.g. that $\alpha(p_1) \le \alpha(p_2)$.
		It holds from \ref{corollary:split_to_alpha} that $\alpha(p_1) \le \as(t) \le \alpha(p_2)$ so with $\alpha$ being non-decreasing it follows
		\[\alpha(0) \le \alpha(p_1) \le \as(t) \le \alpha(p_2) \le \alpha(1) \Rightarrow \as(t) \in [\alpha(0), \alpha(1)]\]
		\item Inverse logic statement of $(ii)$ ($(P \rightarrow Q) \rightarrow (\neg Q \rightarrow \neg P)$).
		\item Natural consequence from Corollary \ref{corollary:split_to_alpha} and Definition \ref{definition:alpha_flow_sets}.
	\end{enumerate}
\end{proof}

At this point we should notice that $\as$, similarly to $x$, depends only on the toll difference $t_1 - t_2$ and whether $t_1 < t_2$ or otherwise.
In order to emphasise on this, let's point out that we could alternatively have defined both $x$ and $\as$ as single variable functions with a domain of values $t_d = t_1 - t_2 \in \R$ and function values as such
\[
	x(t_d) =
	\begin{cases*}
		x((t_d, 0)) & $t_d \ge 0$ \\
		x((0, -t_d)) & $t_d < 0$ \\
	\end{cases*}
\]
We will not utilise this definition as is in this work, however displaying it helps with the intuition that the flow, and consequently $\as$, actually changes as the toll difference does in $\R$.

With that in mind, we will investigate the monotonicity of $\as(t)$ in relation to toll differences (and in extension to latency differences).
For this we will need to compare different tolls that create lower-upper splits in the same edges, or in other words for tolls $t, t^\prime$ to hold that if $t_1 > t_2$ then also $t_1^\prime > t_2^\prime$ and vice-versa.
We will capture this with the following condition
\begin{equation}
	\label{eq:split_property_cond_tolls_0}
	\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} > 0
\end{equation}
where indeed if $t_1 > t_2$ then
\[t_1 > t_2 \Leftrightarrow t_1 - t_2 > 0 \LeftrightarrowArg{(\ref{eq:split_property_cond_tolls_0})} t_1^\prime - t_2^\prime > 0 \Leftrightarrow t_1^\prime > t_2^\prime\]
and likewise we also get $t_1 < t_2 \Leftrightarrow t_1^\prime < t_2^\prime$.
Also note that this property also holds for the respective latencies.

>>>>

In the homogeneous case all players have an equal reaction to tolls, and therefore the effective cost of a player using link $i$ becomes $\ell_i(x_i) + t_i$.
For a given set of tolls $t$, a flow $x$ is a \textit{Wardrop equilibrium for $t$} if $\forall i, j \in N$ with $x_i > 0$ it holds that
\begin{equation*}
	\ell_i(x_i) + t_i \leq \ell_j(x_j) + t_j
\end{equation*}
In that case, all links with $x_i > 0$ have equal effective costs, i.e. there exists some $K > 0$ such that for all those links $i$ it holds that $\ell_i(x_1) + t_i = K$.
From a well-known result from Beckman et al. \cite{beckmann1956studies} and Dafermos and Sparrow \cite{1363388843888284416}, such and an equilibrium for $t$ exists, is unique with regard to costs and can be described by the following inequality.
\begin{lemma}
	\label{lemma:wardrop_equilibrium}
	A flow $x$ is a Wardrop equilibrium for $t$ if and only if for all feasible flows $x^\prime$,
	\[\sum_{i \in N} (\ell_i(x_i) + t_i) \cdot (x_i - x_i^\prime) \leq 0\]
\end{lemma}

We can therefore denote by $x(t)$ the flow occurring on that unique equilibrium for a given toll $t$.
If $t = 0^N$ then the equilibrium is called the \textit{Wardrop equilibrium}.
It's also worth noting that looking at Lemma \ref{lemma:wardrop_equilibrium}, we can see that what actually matters, with regard to the flow, is the relative difference among the tolls, and not their actual values.
To demonstrate this, if we consider an arbitrary $c \in \R_+$ and tolls $t^\prime = t + c$ then for the same flow $x$ and any other flow $x^\prime$ the sum becomes
\begin{flalign*}
	\sum_{i \in N} (\ell_i(x_i) + t_i + c) (x_i - x_i^\prime) &= \sum_{i \in N} (\ell_i(x_i) + t_i) (x_i - x_i^\prime) + c \left(\sum_{i \in N} x_i - \sum_{i \in N} x_i^\prime\right) \\
	&= \sum_{i \in N} (\ell_i(x_i) + t_i) (x_i - x_i^\prime) \leq 0
\end{flalign*}
which makes $x$ the Wardrop equilibrium for $t^\prime$ as well.
The last equality holds because $x_i, x_i^\prime$ are flows of the network and therefore $\sum_{i \in N} x_i = \sum_{i \in N} x_i^\prime = 1$.
Also, this reasoning is still valid for $c < 0$ as long as $t_i + c \ge 0$ for all $i \in N$, or in other words, as long as $c \ge -\min_{i \in N}{t_i}$.

With this observation we can see that the case of $t = 0^N$ is equivalent to any toll instance such that $t_1 = t_2 = \dots = t_n$.
We will therefore simplify our notation and write $t = 0$ when talking about the game without tolls, though we will in fact mean the entire class $\{t = (c)_{i \in N}, c \in \R_+\}$.

Finally for affine latencies we can calculate $x(t)$.
For $\ell_i(x_i) = a_i x_i + b_i$ with $a_i > 0, b_i \geq 0$ and $t \in \R_+^N$, define $N(t) = \{i \in N | x_i(t) > 0\}$.
Since $x(t)$ is an equilibrium for $t$ then for all $i \in N(t)$ we get $\ell_i(x_i) + t_i = K$ for some common effective cost $K$.
By also using the fact that $\sum_{j \in N(t)} x_i = 1$ we solve the equations with regard to $K$ and eventually get for all $i \in N(t)$
\begin{equation}
	\label{eq:homogeneous_x_i}
	x_i(t) = \frac{1 + \sum_{j \in N(t)}\frac{b_j + t_j - b_i - t_i}{a_j}}{\sum_{j \in N(t)}\frac{a_i}{a_j}}
\end{equation}

@@

For homogeneous players, from the work of Harkes et al. \cite[Example 4.2]{Harks_2019}, we know that uniqueness of $t^*$ is guaranteed only when $x_i(0) > 0$ for all $i \in N$, a property called the \textit{full Wardrop support assumption}.
This is seemingly not as much restrictive in practice, as there would be little motivation to add tolls to a route with no traffic.
From the same work we also get that if the full Wardrop support assumption holds, then $t^*$ is unique \cite[Lemma 3.3]{Harks_2019} and $x_i(t^*) > 0$ and $t_i^* > 0$ for all $i \in N$ \cite[Lemma 3.2]{Harks_2019}.

Also, for affine latencies, we can calculate the best response functions $B_i(t_{-i})$.
For each link owner $i$, by solving first order conditions on $\Pi_i(t_i, t_{-i})$ for $t_i$ we get
\begin{equation}
	\label{eq:homogeneous_br_i}
	B_i(t_{-i}) = \frac{1 + \sum_{j \ne i}\frac{b_j + t_j - b_i}{a_j}}{\sum_{j \ne i}\frac{2}{a_j}}
\end{equation}

@@

To describe more properties of homogeneous pricing games we will need the following crucial Lemma.
\begin{lemma}
	\label{lemma:tolls_diff}
	Let $(N, \ell, 1)$ be a homogeneous pricing game, and let $D_i$ a function for each link $i$ where $D_i(t_{-i}) = B_i(t_{-i}) - t_{-i}$, a vector of $t_i - t_j$ values for all $t_j \in t_{-i}$.
	Then $D_i$ is decreasing with regard to any $t_j \in t_{-i}$.
\end{lemma}

\begin{proof}
	For any link $i$ and any $t_j \in t_{-i}$ consider the respective element of $D_i$, which is $B_i(t_{-i}) - t_j$.
	From formula \ref{eq:homogeneous_br_i} after some calculations we get
	\[
		B_i(t_{-i}) - t_j = \left(\frac{1}{\sum_{k \ne i} \frac{2a_j}{a_k}} - 1\right)t_j + \frac{1 + \frac{b_j - b_i}{a_j} + \sum_{k \ne i, j}\frac{b_k + t_k - b_i}{a_k}}{\sum_{k \ne i} \frac{2}{a_k}}
	\]
	which is decreasing with regards to $t_j$ if and only if its coefficient is negative.
	Indeed, since $a_i > 0$ for all $i$, we get
	\[
		\frac{1}{\sum_{k \ne i} \frac{2a_j}{a_k}} - 1 = \frac{1}{2 \left(1 + \sum_{k \ne i, j} \frac{a_j}{a_k}\right)} - 1 \leq \frac{1}{2} - 1 < 0
	\]
\end{proof}

@@

Consider a $([2], \ell, \alpha)$ heterogeneous parallel game with links $[2] = \{1, 2\}$ such that $x_1(0), x_2(0) > 0$ with tolls $t = (t_1, t_2)$ assigned to them and  $x(t) = (x_1(t), x_2(t))$ the Nash equilibrium for $t$.
Without loss of generality we assume $t_1 > t_2$ which from Lemma \ref{lemma:latencies_tolls} leads to $\ell_1(x_1(t)) < \ell_2(x_2(t))$.
For the $2$ edges of the game we introduce the term money sensitivity split $\as(t)$ as the value of $\alpha$ for which if any player $p$ has $\alpha(p)=\as(t)$ then that player sees the $2$ edges' total latencies as equal.
More specifically, $\as(t)$ is the value of the distribution function $\alpha$ for which it holds
\[\ell_1(x_1(t)) + \as(t) \cdot t_1 = \ell_2(x_2(t)) + \as(t) \cdot t_2\]
Solving for $\as$ we get
\[\as(t) = \frac{\ell_2(x_2(t)) - \ell_1(x_1(t))}{t_1 - t_2}\]
\\
Before we get into a more formal definition and description of $\as$, it'd help to first discuss the nature of the split that $\as$ captures.
Regardless of whether there exists a player $p$ such that $\alpha(p) = \as(t)$, it still holds that
\begin{itemize}
	\item if $\alpha(p) < \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 < \ell_2(x_2(t)) + \alpha(p \cdot) t_2$, thus $p$ is on edge $1$
	\item if $\alpha(p) > \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 > \ell_2(x_2(t)) + \alpha(p) \cdot t_2$, thus $p$ is on edge $2$
	\item if $\alpha(p) = \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 = \ell_2(x_2(t)) + \alpha(p) \cdot t_2$, thus $p$ is either on edge $1$ or $2$
\end{itemize}
Remember that we have assumed that $t_1 > t_2 \Rightarrow \ell_1(x_1(t)) < \ell_2(x_2(t))$.
Therefore the flow passing through the faster edge $1$ is contained with players where $\alpha(p) \le \as(t)$, while the flow in the cheaper edge $2$ is contained with players where $\alpha(p) \ge \as(t)$.
Since the players are sorted in increasing order according to $\alpha$, it helps to view the players in the first case as the "lower" part of the split and respectively the players in the second case as the "upper" part of the split.
If it helps with the intuition, alternative split labels could be rushed-relaxed or rich-poor.
Table \autoref{table:split_summary} provides of a summary for each part of the split

@@

\begin{definition}
	\label{definition:split_function}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
	We define the \textit{money sensitivity split function} $\as^{(i, j)}: \{t \in \R_+^N|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
	\[\as^{(i, j)}(t) = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j}\]
\end{definition}

For $t_i = t_j$ any split value will work, so the function is not well-defined for this case.
We will also give a more formal definition to the lower-upper split intuition we described above.
\begin{definition}
	\label{definition:split_lower_upper}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
	Assuming w.l.o.g. that $t_i > t_j$, we define as \textit{lower split} the (possibly empty) flow $x_i(t)$ and as \textit{upper split} the (possibly empty) flow $x_j(t)$. 
\end{definition}

\begin{corollary}
	\label{corollary:split_to_alpha}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$.
	It holds that
	\begin{itemize}
		\item $\alpha(p) \le \as^{(i, j)}(t)$, for all players $p$ in the lower split
		\item $\alpha(p) \ge \as^{(i, j)}(t)$, for all players $p$ in the upper split
	\end{itemize}
\end{corollary}

\begin{proof}
	Let again w.l.o.g. assume $t_i > t_j$, making by definition \ref{definition:split_lower_upper} a player $p$ in the lower split be in link $i$.
	Since $x$ is a Nash equilibrium we have
	\begin{align*}
		c_i^p(t) &\le c_j^p(t) \Rightarrow \ell_i(x_i(t)) + \alpha(p) \cdot t_i \le \ell_j(x_j(t)) + \alpha(p) \cdot t_j \\
		&\RightarrowArg{t_i > t_j} \alpha(p) \le \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j} \RightarrowArg{\ref{definition:split_function}} \alpha(p) \le \as^{(i, j)}(t)
	\end{align*}
	Similarly we can show that $\alpha(p) \ge \as^{(i, j)}(t)$, for all players $p$ in the upper split.
\end{proof}

At this point in our analysis, we will need to describe the notion of the lowest and highest $\alpha$ value in a flow of players.
In general, since we're working with a Lebesque-measurable flow, it is natural to not bother with distinguishing between a flow $[0, x_1]$ or $[0, x_1)$, as the player $x_1$ can be arbitrarily placed at any link without affecting the game.
In a heterogeneous setting, however, the player's $\alpha(x_1)$ might deterministically put him in a specific link depending on how $\alpha$ is defined, so we need to be careful with our notation.
We will define the $\alpha$ values of a link's flow in a set and then use border bounds which covers both open and closed intervals.

One difficulty we need to consider with this approach are cases where $t_i = t_j$ for some links $i, j \in N$.
For such tolls $t$, even though $x(t)$ is uniquely defined, we get for all players $p$ that $c_i^p(t) = c_j^p(t)$, and thus the players in links $i$ and $j$ can be put arbitrarily in any of the two, regardless of the $\alpha$ value.
Even if we attempted to put them orderly, it actually matters which edge we will put first, as the link might have different flow volume resulting in different $\alpha$ values within.
For this reason we will assume our sets contain all possible $\alpha$ values of any player that might use a link.
We therefore loose the information about the actual flow splits among those links and keep only the ones among links with different toll values (and in consequence different latencies, Lemma \ref{lemma:latencies_tolls}).
Still, even with this information loss, we can still observe that
\begin{enumerate}
	\item The notion of $\as$ as the $\alpha$ value that views two links as equal is still valid, since such a player will also view as equal any other link with the same toll value as any of the initial two.
	\item If we limit our scope to only include the links with equal tolls, we actually get a homogeneous sub-game for the total flow in those links.
\end{enumerate}
With the above we arrive at the following definition.

\begin{definition}
	\label{definition:alpha_flow_sets}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ and $x(t)$ the Nash equilibrium for $t$.
	We define as $A_i(t)$ the set of all possible $\alpha(p)$ values of players $p$ using link $i$ in the Nash equilibrium for $t$.
	More formally, we define a set function $A_i: \R_+^N \rightarrow \mathcal{P}(\R_+)$, where $\mathcal{P}(\R_+)$ is the powerset of $\R_+$, such that
	\[A_i(t) = \{\alpha(p)|p \text{ in edge } j \text{ for } x(t) \text{ where } t_j = t_i\}\]
\end{definition}

Notice that with this definition it follows that $A_i(0)$ is the entire domain of $\alpha$ for all $i \in N$.
We continue with describing some basic properties around the values of $\as$.

%We ignore all $\alpha(x_i(0))$ values in order to avoid any confusion, since they are arbitrarily placed in any edge and their $\alpha$ value could change the sets' properties.
%It doesn't affect our analysis, however, since having a split on that player is only possible for $t = 0$ and $\as(0)$ is undefined, plus as we'll show in the next section neither it's limit exists, making the $\alpha$ value of player $x_i(0)$ (in each assumingly split case) irrelevant.

@@

\begin{lemma}
	\label{lemma:split_basic}
	Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t$ where $t_i \ne t_j$ and $x_i(t), x_j(t) > 0$ for some links $i, j \in N$.
	Then the following hold:
	\begin{enumerate}[(i)]
		\item $\as^{(i, j)}(t) > 0$
		\item $\as^{(i, j)}(t) \in [\alpha(0), \alpha(1)]$
		%\item if $\as^{(i, j)}(t) < \alpha(0)$ (or $\as^{(i, j)}(t) > \alpha(1)$) then $x(t) = (0, 1)$ (or $(1, 0)$)
		\item if $\ell_i(x_i(t)) < \ell_j(x_j(t))$ then
		$\sup A_i(t) \le \as^{(i, j)}(t) \le \inf A_j(t)$
	\end{enumerate}
\end{lemma}

\begin{proof}
	$ $ % Just to make a line break after "Proof".
	\begin{enumerate}[(i)]
		\item Trivial application of Lemma \ref{lemma:latencies_tolls}.
		Since we have $t_i \ne t_j$ it follows that $\ell_i(x_i(t)) \ne \ell_j(x_j(t))$ and therefore $\as^{(i, j)}(t) \ne 0$.
		Then we only need to notice that $\ell_i(x_i(t)) < \ell_j(x_j(t)) \Leftrightarrow t_i > t_j$ and we get $\as^{(i, j)}(t) > 0$ from Definition \ref{definition:split_function}.
		\item Since $x_i(t), x_j(t) > 0$ then $\exists p_i, p_j \in [0, 1]$ each on a different link, for which we assume w.l.o.g. that $\alpha(p_i) \le \alpha(p_j)$.
		Then from Corollary \ref{corollary:split_to_alpha} It holds that $\alpha(p_i) \le \as^{(i, j)}(t) \le \alpha(p_j)$.
		With $\alpha$ being non-decreasing it follows
		\[\alpha(0) \le \alpha(p_i) \le \as^{(i, j)}(t) \le \alpha(p_j) \le \alpha(1) \Rightarrow \as(t) \in [\alpha(0), \alpha(1)]\]
		%\item Inverse logic statement of $(ii)$ ($(P \rightarrow Q) \rightarrow (\neg Q \rightarrow \neg P)$).
		\item Natural consequence from Corollary \ref{corollary:split_to_alpha} and Definition \ref{definition:alpha_flow_sets}.
	\end{enumerate}
\end{proof}

At this point we should notice that $\as$, similarly to $x$, depends only on the toll differences and on the toll ordering of the links.
In order to emphasise on this, let's restrict ourselves to $2$ links and point out that we could alternatively have defined both $x$ and $\as$ as single variable functions with a domain of values $t_d = t_1 - t_2 \in \R$ and function values as such
\[
	x(t_d) =
	\begin{cases*}
		x((t_d, 0)) & $t_d \ge 0$ \\
		x((0, -t_d)) & $t_d < 0$ \\
	\end{cases*}
\]
We will not utilise this definition as is in this work as it gets more complex for games with $n$ links, however displaying it helps with the intuition that the flow, and consequently $\as$, actually changes as the toll differences do in $\R^{N - 1}$.
